### 2022-06-22 paper.Rmd
fix

# Plot the results, by N
ldf <- ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  )

ldf %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16)

>>>>

# Plot the results, by N
ldf %>% 
  group_by(method, Objective, N) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(method != "random") %>% 
  mutate(
    Objective = ordered(
      Objective, 
      levels = c("means", "sd", "skew", "kur", "cor"),
      labels = c("M", "SD", "Skew", "Kurtosis", "Correlation"))
  ) %>%
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(linetype = method), size = .85) + 
  facet_grid(rows = vars(Objective), scales = "free") + 
  ylab("Mean discrepancy") +
  theme_bw(base_size = 16)
